Automated Verification Applied to Stand-alone Solar Photovoltaic Systems: Optimal Sizing and Project Validation

### 2019-07-03 Tex/Old text/chapters/conclusion.tex
thesis updated text

We have described and evaluated an automated verification method to check whether a given PV system meets its specification using software model checking techniques. We have considered five case studies from real PV systems deployed in five different sites, ranging from $700$ W to $1,200$ W; and three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker). Although the verification method proposed takes longer than simulation methods, it is able to present details that lead to failures in a PV system that is not a feature presented in commercial simulation tool. In particular, the proposed method was successful in finding sizing errors and indicating in details. Related to the verification engines comparative, the ESBMC with the Z3 solver executed in the incremental configuration presented the better performance (around four times faster than CBMC), used less RAM memory (less than 2GB when compared to 9.2GB of CBMC and 19.2GB of CPAchecker), and all the results were sound because the PV owners and the monitoring system validated the possible flaws that the system could be presenting in the field.
%New tests must be performed, in an improved setup (i.e., better computing performance) with the goal of obtaining verification results in shorter times than the ones obtained in this study. 
As future work, we will also consider other types of renewable energy and even hybrid ones to allow our method to verify typical rural electrification.

@@

As future work, the authors plan to improve the power reliability analysis, 
to address the restriction to only allow automated synthesis of 
riverside communities in the Amazonas state (Brazil), and to 
validate some cases with deployed PV systems in isolated communities.

>>>>

\section{Main Contributions}

We have described and evaluated an automated verification method to check whether a given PV system meets its specification using software model checking techniques. We have considered five case studies from real PV systems deployed in five different sites, ranging from $700$ W to $1,200$ W; and three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker). Although the verification method proposed takes longer than simulation methods, it is able to present details that lead to failures in a PV system that is not a feature presented in commercial simulation tool. In particular, the proposed method was successful in finding sizing errors and indicating in details. Related to the verification engines comparative, the ESBMC with the Z3 solver executed in the incremental configuration presented the better performance (around four times faster than CBMC), used less RAM memory (less than 2GB when compared to 9.2GB of CBMC and 19.2GB of CPAchecker), and all the results were sound because the PV owners and the monitoring system validated the possible flaws that the system could be presenting in the field.
%New tests must be performed, in an improved setup (i.e., better computing performance) with the goal of obtaining verification results in shorter times than the ones obtained in this study.

@@

\section{Future Work Directions}
create a research group in automated verification applied to electrical systems
improve mathematical models

Automated verification: As future work, we will also consider other types of renewable energy and even hybrid ones to allow our method to verify typical rural electrification.

Synthesis: As future work, the authors plan to improve the power reliability analysis, 
to address the restriction to only allow automated synthesis of 
riverside communities in the Amazonas state (Brazil), and to 
validate some cases with deployed PV systems in isolated communities.

\section{Concluding Remarks}

### 2019-07-03 Tex/Old text/main.tex
thesis updated text

\input{abstract}

%\chapter*{Dedication}
%To mum and dad
%
%\chapter*{Declaration}
%I declare that..
%
\chapter*{Acknowledgements}
I want to thank...

@@

\listoftables

\chapter{Introduction}
\input{chapters/introduction}

@@

\chapter{Experimental Evaluation}
\input{chapters/chapter04}

\chapter{Conclusion and Future Work}
\input{chapters/conclusion}

\appendix
\chapter{Appendix Title}
\input{chapters/appendix}

%\printbibliography
\bibliography{trindadeThesis}{}

>>>>

\input{2ndcover}
\thispagestyle{empty}
\pagenumbering{gobble}

\input{fichacatalog}
%\thispagestyle{empty}
\newpage

\input{abstract}
\pagestyle{empty}
%\thispagestyle{empty}

\input{resumo}
%\thispagestyle{empty}

%\chapter*{Dedication}
%To mum and dad
%
%\chapter*{Declaration}
%I declare that..
%
\chapter*{Acknowledgements}
(It is not possible to get here without the help of several people. I hope I have not forgotten any and do no wrong).

I would like to thank God (for the gift of life); Solange and Louise (without the patience and support of my family I could not be here); my parents and grandparents; Lucas (for having believed in me and for the patience); the Electricity Department at UFAM (for the support); Professors Feitosa, Marco Cristo and Barreto from IComp (support and advice); IT support team from IComp (Virtual Machine maintenance); secretary people from IComp (for the administrative support); the financial support from FAPEAM, British Council/Newton Fund and Fundação Amazonas Sustentável; Davide Poggio from University of Sheffield for the HOMER Pro license (Research England QR GCRF Institutional Allocation); and Coventry University team (Elena, Kojo, and Ross for the opportunity to use field deployed photovoltaic solar systems).

\pagestyle{empty}

@@

\listoftables
\newpage 
\input{abbreviations}

\chapter{Introduction}
\pagenumbering{arabic}
\pagestyle{fancy}
\fancyhead{}
\fancyhead[RO,LE]{Automated Verification Applied to Stand-alone Solar Photovoltaic Systems}
\fancyfoot{}
\fancyfoot[LE,RO]{\thepage}
\fancyfoot[CO,CE]{Chapter \thechapter}
\fancyfoot[LO,RE]{A. B. Trindade}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}
\input{chapters/introduction}

@@

\chapter{Automated Formal Verification of Stand-Alone Solar PV Systems}
\input{chapters/chapter04}

\chapter{Automated Formal Synthesis Optimization Method for Sizing of Stand-Alone Solar PV Systems}
\input{chapters/chapter05}

\chapter{Conclusions}
\fancyfoot[CO,CE]{Conclusions}
\input{chapters/conclusion}

\appendix
\chapter{List of Publications}
\fancyfoot[CO,CE]{Appendix}
\input{chapters/appendix}

\fancyfoot[CO,CE]{References}
%\printbibliography
\renewcommand\bibname{References}
\bibliography{trindadeThesis}{}
